Wibbly Wobbly Timely Wimely Questions: \\Classifying Timely And Timeless Questions

### 2021-07-15 paper/main.tex
up to abstract and definition

@@

\begin{abstract}
	Classifying timely and timeless questions can be a useful task for natural
	language processing. We present a method for determining if a question is
	timely or timeless using a pretrained BERT model and the Google NQ dataset.
	Past revisions of the source Wikipedia page are retrieved and the answers are
	compared to see how they change over time. We show that we can find timely
	questions with greater than chance probability and timeless questions with
	high accuracy using our method.

\end{abstract}

\section{Problem Overview}
\label{overview}
Question answering (QA) is a fundamental task in natural language processing.
The objectives are to understand questions posed in natural language and
retrieve relevant information within a database or text to answer them. The
answers to some questions remain unchanged and static regardless of the time
they are asked. We will refer to these questions as timeless questions. As
examples, the answers to the questions “When was the Magna Carta signed” and
“Who was the first person to walk on the moon” do not change over time. On the
other hand, some questions will have different answers based on when they are
asked, and we will refer to these as timely questions. To illustrate, the answer
to “Who won the world cup” will change every four years, and the answer to “How
many farms are there in Alaska” will vary depending on how many Alaskan farms
exist at the asking time.

The purpose of our project is to build a pipeline that determines the
“timeliness” of questions, as understanding whether a question is timely or
timeless could be useful for accurate question answering. When an individual
asks a timely question, they would expect the system to return the most recent
answer. Detecting timeliness in queries is a nifty skill for voice assistant
software and chatbots; if a question is understood to be timely, updated answers
could be routinely checked to provide accurate results for possible future
queries.

\subsection{Related Work}

@@

\subsection{Dataset}
\label{dataset}
We used Google’s Natural Questions (NQ) dataset \cite{nqdataset}. The dataset
has been used for open-domain question answering research, and is “the first
large publicly available dataset to pair real user queries with high quality
annotations of answers in documents”. It consists of 307,373 anonymized natural
questions asked via the Google search engine, and each question is paired with
the full HTML markup of a Wikipedia page. Human annotators have marked the
location of long and short answers to each question. A model that is trained on
the NQ dataset is required to read the full Wikipedia article, and locate the
answers. From our analysis, we estimate that less than 10\% of the questions
were timely questions.

@@

\section{Future Work}
With a longer project timeline, we would have liked to retrain a BERT model
ourselves on the NQ dataset to get a more accurate model. In addition, once we
have a more accurate set of timely and timeless questions, we would train a
language model to classify questions based on their timeliness.

\section{Contributions}
\subsection{Vatsal Agarwal}
Vatsal helped with dataset processing and analysis, as well as the presentation
and paper work.
\subsection{Pauline Comising}
Pauline ran the Google Trends baseline, helped with Wikimedia API integration,
implemented BLEU score calculations, and helped with presentation and paper
writing.
\subsection{Harish Kumar}
Harish ran the Google Trends baseline. He also helped with presentation and
paper writing.
\subsection{Madhava Paliyam}
Madhava ran the BERT-SQUAD model on the train and development datasets. He
implemented the comparisons using the {\tt fuzzywuzzy} package. He also helped
with the analysis.

\subsection{Nikhil Pateel}
Nikhil worked on the Google Trends baseline, Wikimedia API integration, as well
as presentation and paper preparation.

>>>>

\newcommand{\question}[1]{``#1''}
\newcommand{\ans}[1]{\underline{#1}}

@@

\begin{abstract}
  Question answering datasets are often tied to a particular time and knowledge base.
  %
  This paper examines whether questions in common \abr{qa} datasets
  are timeless (the answer is invariant to changing the knowledge
  base) or timely (the answer changes when the knowledge base
  changes).
  %
  After identifying whether a question is timeless or timely and
  analyzing what makes a question timely, we build a classifier to
  detect these questions automatically, allowing \abr{qa} systems to
  detect when their knowledge base may be stale.
\end{abstract}

\section{Problem Overview}
\label{overview}
Question answering (QA) is a fundamental task in natural language processing.
The objectives are to understand questions posed in natural language and
retrieve relevant information within a database or text to answer them. The
answers to some questions remain unchanged and static regardless of the time
they are asked. We will refer to these questions as timeless questions. As
examples, the answers to the questions \question{When was the Magna Carta signed} and
\question{Who was the first person to walk on the moon} do not change over time. On the
other hand, some questions will have different answers based on when they are
asked, and we will refer to these as timely questions. To illustrate, the answer
to \question{Who won the world cup} will change every four years, and the answer to \question{How
many farms are there in Alaska} will vary depending on how many Alaskan farms
exist at the asking time.

The purpose of our project is to build a pipeline that determines the
``timeliness'' of questions, as understanding whether a question is timely or
timeless could be useful for accurate question answering. When an individual
asks a timely question, they would expect the system to return the most recent
answer. Detecting timeliness in queries is a nifty skill for voice assistant
software and chatbots; if a question is understood to be timely, updated answers
could be routinely checked to provide accurate results for possible future
queries.

\section{Mutatis Mutandis}
\label{sec:definition}

Before beginning our empirical analysis, we first define two broad
types of questions: timeless and timely questions.
%
More formally, a {\bf timeless} question~$q^{s}$ is a question for
which an answer~$a$ is consistent regardless of when~$t$ a
dataset~$\mathcal{D}_t$ was gathered.
%
In other words, the answer is static (or not present) but does not
change when an answer is found from a \abr{qa} system~$f$ on a
dataset:\footnote{For the ease of exposition we ignore \abr{qa}
mistakes and variation in answer form.  A more rigorous definition
would define probabilities and answer equivalence sets.}
%
\begin{equation}
  \forall_{t,t'} \left[ f(q^{s}, \mathcal{D}_t) = f(q^{s},
    \mathcal{D}_{t'}) \vee f(q^{s}, mathcal{D}_{t'}) = \emptyset
    \right].
\end{equation}
%
However, a timely question $q^{v}$ does vary:
%
\begin{equation}
  \exists_{t,t} s.t. f(q^{v}, \mathcal{D}_t) \not = f(q^{v},
  \mathcal{D}_{t'}).
\end{equation}

@@

\subsection{Dataset}
\label{dataset}

\jbgcomment{Cite followon datasets}

We used Google’s Natural Questions (NQ) dataset \cite{nqdataset}. The
dataset has been used for open-domain question answering research, and
is “the first large publicly available dataset to pair real user
queries with high quality annotations of answers in documents”. It
consists of 307,373 anonymized natural questions asked via the Google
search engine, and each question is paired with the full HTML markup
of a Wikipedia page. Human annotators have marked the location of long
and short answers to each question. A model that is trained on the NQ
dataset is required to read the full Wikipedia article, and locate the
answers. From our analysis, we estimate that less than 10\% of the
questions were timely questions.

Natural Questions is unique becuase it has been updated twice: once by
\abr{nq}'s original authors for the Efficient \abr{qa} competition and
by \abr{ai2} by a new collection of questions from Google.

@@

\section{Related Work}

\section{Conclusion and Future Work}
With a longer project timeline, we would have liked to retrain a BERT model
ourselves on the NQ dataset to get a more accurate model. In addition, once we
have a more accurate set of timely and timeless questions, we would train a
language model to classify questions based on their timeliness.
